Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-27 discussion.tex
working

{\bf Social-psychological incentives} and {\bf voting and ranking} are supported
through starring. This mechanism was employed often by our test
audience. \gordon{actually, the notebook tree quickly became so unwieldy that
no one uses this.} An obvious next step would be to enhance recommendations using
relationships discovered by static and dynamic code analysis. This may be
considered both within and across collections of scripts (the latter being
similar to Vistrails' enhanced recommendations by clustering multiple
workflows).  It seems valuable to know which packages are frequently used
together, or appear in proximity to a certain record types or data feeds.  In
general, trivial or passive mechanisms to collect data for recommendations are
essential.

@@

{\bf Caching.}
An important consideration is how and where to introduce caching
in RCloud's distributed computation model. Caching can dramatically
improve performance in a way that is otherwise transparent to
application program semantics \cite{Callahan:2006:VVM, Guo:2010:TPI}.
Though caching is usually implicit, in some environments, such as
Vistrails, programmers may also have some explicit control over cache
management. This may be desirable to ensure the repeatability of
computations that rely on volatile or unreliable data sources.
For example, the stock ticker use case is one for which the data
might temporarily become unavailable, so caching could improve
reliability and consistency of results. Alternatively, in situations
involving relatively expensive computation (for example, analysis of large
text corpora, clustering multivariate time series or deep learning algorithms)
caching may be essential to adequate performance. Currently we would
program this in RCloud by explicitly saving an analysis in a persistent database,
but it seems better to implement this capability in a general purpose associative
cache, instead of application-specific libraries. We envision cache management
being implemented in a new middle layer to be added in the future.

>>>>

{\bf Social-psychological incentives} and {\bf voting and ranking} are supported
through starring. This mechanism was employed often by our test
audience. \gordon{actually, the notebook tree quickly became so unwieldy that
no one uses this.} An obvious next step would be to enhance recommendations using
relationships discovered by static and dynamic code analysis. This may be
considered both within and across collections of scripts (the latter being
similar to VisTrails' enhanced recommendations by clustering multiple
workflows).  It seems valuable to know which packages are frequently used
together, or appear in proximity to a certain record types or data feeds.  In
general, trivial or passive mechanisms to collect data for recommendations are
essential.

@@

{\bf Caching.}
An important consideration is how and where to introduce caching
in RCloud's distributed computation model. Caching can dramatically
improve performance in a way that is otherwise transparent to
application program semantics \cite{Callahan:2006:VVM, Guo:2010:TPI}.
Though caching is usually implicit, in some environments, such as
VisTrails, programmers may also have some explicit control over cache
management. This may be desirable to ensure the repeatability of
computations that rely on volatile or unreliable data sources.
For example, the stock ticker use case is one for which the data
might temporarily become unavailable, so caching could improve
reliability and consistency of results. Alternatively, in situations
involving relatively expensive computation (for example, analysis of large
text corpora, clustering multivariate time series or deep learning algorithms)
caching may be essential to adequate performance. Currently we would
program this in RCloud by explicitly saving an analysis in a persistent database,
but it seems better to implement this capability in a general purpose associative
cache, instead of application-specific libraries. We envision cache management
being implemented in a new middle layer to be added in the future.
